%------------------------
  % Resume in Latex
  % Name: Ayush Soni
  % GitHub: https://github.com/ayushsoni1010
  % License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\hypersetup{%
  colorlinks=true,% hyperlinks will be colored
  linkcolor=blue,% hyperlink text will be green
  linkbordercolor=blue,% hyperlink border will be red
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEduheading}[4]{
\vspace{2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    {#1} & #2 \\
    \textit{\small#3} & \textit{\small #4}\\
    % \textit{\small#5} \\
  \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%

\begin{document}

% ---------- HEADING ----------

\begin{center}
\textbf{\Huge \scshape Ayush Soni} \\ \vspace{10pt}
\href{tel:9644963410}{+91 9644963410} $|$
{Pune, India} $|$
{Full Stack Developer} $|$
\href{mailto:ayushsoni1010.work@gmail.com}{ayushsoni1010.work@gmail.com} \\ \vspace{3pt}

\href{https://linkedin.com/in/ayushsoni1010}{\underline{linkedin.com/in/ayushsoni1010}} $|$
\href{https://github.com/ayushsoni1010}{\underline{github.com/ayushsoni1010}} $|$
\href{https://twitter.com/ayushsoni1010}{\underline{twitter.com/ayushsoni1010}} $|$
\href{https://ayushsoni1010.com}{\underline{ayushsoni1010.com}}
\end{center}


% ---------- PROGRAMMING SKILLS ----------

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
      \textbf{Languages}{: \hfill Javascript, Typescript, Python, SQL } \\
      \vspace{3pt}\textbf{Libraries/Frameworks}{: \hfill React/React Native/Next.js, Vue/Nuxtjs, Redux/Zustand, Nodejs/Express, FastAPI, Socket.io} \\
      \vspace{3pt}\textbf{UI Component Libraries/CSS}{: \hfill Chakra UI, Shadcn UI, Radix UI, Ant Design, Material UI, styled-components, TailwindCSS, Framer} \\
      \vspace{3pt}\textbf{Databases/Servers}{: \hfill MongoDB, MySQL, PostgreSQL, Redis, Prisma, Drizzle, Nginx} \\
      \vspace{3pt}\textbf{Platforms/Tools}{: \hfill AWS, Docker, Firebase, Supabase, Vercel/Netlify, Webpack, Vite, GitHub Actions} \\
      \vspace{3pt}\textbf{AI/Tools}{: \hfill LLMs, RAG, AI Agents, MCP, SSE, Prompt Engineering, LangChain, Vector DBs, Cursor, Warp} \\
      \vspace{3pt}\textbf{Others}{: \hfill WebSockets/REST/GraphQL, Jest/Cypress/Storybook, Puppeteer, Chartjs, Strapi, Figma, Swagger, Postman}
      }}
\end{itemize}


% ---------- EXPERIENCE ----------

\section{Experience}
\resumeSubHeadingListStart

% ------------------------
\resumeSubheading
{\textbf{\href{https://attentions.ai}{Attentions AI}\hspace{5pt}}{{[Next.js, AI Agents, Pub-Sub, WebSockets, MCP]}}}{(Onsite) Pune, India}
{\textbf{Software Development Engineer I – Full-time}}{October 2024 -- Present}
\resumeItemListStart
\resumeItem{Built 4 production micro-frontends(Artigen, Connect, Docu, Lumina) for Q\&A on documents, call centers, e-commerce solution.}
\resumeItem{Improved app performance by 40\%, implemented WebSocket streaming, built markdown wrapper, \& real-time pub-sub systems.}
\resumeItem{Developing enterprise Chat SDK with voice, numerous AI agents, MCP connectors and integrations for the B2B client workflows.}
\resumeItemListEnd
% ------------------------


% ------------------------
\resumeSubheading
{\textbf{\href{https://go2work.com}{Go2work}\hspace{5pt}}{{[TypeScript, Next.js, Firebase, AWS, Shadcn UI]}}}{(Remote) Houston, Texas, United States}
{\textbf{Frontend Engineer – Full time}}{November 2023 -- October 2024}
\resumeItemListStart
\resumeItem{Built hiring platform dashboard from scratch using TypeScript/Next.js, architected reusable component library with Shadcn UI.}
\resumeItem{Optimized application performance by 70\% through code refactoring, UI improvements, and chaos engineering implementation.}
\resumeItem{Delivered real-time WebSocket chat system, push notifications, and secure Firebase authentication for seamless user workflows.}
\resumeItemListEnd
% ------------------------


% ------------------------
\resumeSubheading
{\textbf{\href{https://fifhtry.com}{FifthTry}\hspace{5pt}}{{[JavaScript, React, fastn]}}}{(Remote) Bengaluru, India}
{\textbf{Developer Relations Engineer – Full time}}{April 2023 -- September 2023}
\resumeItemListStart
\resumeItem{Built 10+ sample applications with fastn framework, contributed to Rust-based core development, driving developer adoption.}
\resumeItem{Developed comprehensive documentation platform, delivered technical workshops to 5000+ developers across multiple cities.}
\resumeItem{Organized 12+ nationwide community events, grew developer community by 300\%, established key partnership relationships.}
\resumeItemListEnd
% ------------------------


% ------------------------
\resumeSubheading
{\textbf{\href{https://magic.app}{Magic}\hspace{3pt}}{{[NuxtJS, NodeJS, Parse Server]}}}{(Remote) Delhi, India}
% {Magic}{Remote, Delhi}
{\textbf{Product Engineer – Intern}}{January 2023 -- March 2023}
\resumeItemListStart
\resumeItem{Engineered SaaS dashboard for 10+ Slack communities, eliminating 60\% of platform switching and boosting engagement rates.}
\resumeItem{Developed authentication system, password recovery flows, and created the sitemaps using NuxtJS and Parse Server integration.}
\resumeItem{Delivered community events module, implemented LogRocket analytics integration that decreased bug resolution time by 60\%.}
\resumeItemListEnd
% ------------------------


% ------------------------
\resumeSubheading
{\textbf{\href{https://economize.cloud}{Economize}\hspace{3pt}}{{[Vue, Go]}}}{(Remote) Bengaluru, India}
% {Economize}{Remote, Bengaluru}
{\textbf{Software Engineer – Intern}}{October 2021 -- November 2022}
\resumeItemListStart
\resumeItem{Developed cloud cost optimization SaaS dashboard serving 500+ enterprise clients across AWS and GCP platforms using Vue.js.}
\resumeItem{Delivered 40\% UX improvement of documentation, AWS/GCP report tables, and implemented Storybook + Strapi CMS setup.
}
\resumeItem{Created component library with 15+ reusable elements using Ant Design and Chart.js, accelerating team development by 30\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd
% ------------------------


% ---------- PROJECTS ----------

\section{Projects}

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/ayushsoni1010/inklink}{Inklink}\hspace{5pt}}{{[Nextjs, TypeScript, Nodejs, MongoDB, Shadcn UI]}}}{}
\resumeItemListStart
\resumeItem{Building a product that simplifies content creation by posting to multiple platforms with a single click in no time.}
\resumeItem{Integrating multiple platforms in one place, helping creators save time on writing once and share everywhere.}
\resumeItem{Users can engage with content by liking, posting, sharing, subscribing to newsletters, building a creator portfolio.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/ayushsoni1010/mapsearchify}{MapSearchify}\hspace{5pt}}{{[Vue, NuxtJS, Algolia, TypeScript, MapboxGL.js, Tailwind]}}}{}
\resumeItemListStart
\resumeItem{It is a web-based application that utilizes the MapboxGL Maps API to provide location-based search functionality.}
\resumeItem{Many people are located on Map like a Snapchat Map feature with an optimized search utility built using Algolia.}
\resumeItem{Users can search for nearby places and filter results by country, city, name, company and maps the user's location.}
\resumeItemListEnd
\resumeSubHeadingListEnd


% ---------- EDUCATION ----------

\section{Education}
\resumeSubHeadingListStart
\resumeEduheading
{Medi-Caps University}{Indore, Madhya Pradesh, India}
{Bachelor of Technology in Computer Science and Engineering}{CGPA: 8.7/10}
\resumeSubHeadingListEnd



% ---------- Awards, Community and Volunteer Experience ----------
\section{Awards, Community \& Volunteer Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
      \resumeItemListStart
              \resumeItem{\textbf{\href{https://mlh.io}{Major League Hacking}}{: Participated in multiple hackathons organized by MLH like Abracadabra Hacks, MLH INIT, Local Hack Day, Design-a-thon, Wittyhacks and attended MLH HackCon IN conference in-person in Delhi.}} \vspace{3pt}
              \resumeItem{\textbf{\href{https://studentambassadors.microsoft.com/}{Microsoft Learn Student Ambassador}}{: Conducted hands-on sessions on Git, GitHub, frontend development, open source contribution, taught best practices and promoted Hacktoberfest, and built hands-on projects.}} \vspace{3pt}
              \resumeItem{\textbf{Mentor at {\href{https://hackacode.anyonecanco.de}{AnyoneCanCo.de}}, {\href{https://hackthenorth.com}{HackTheNorth}}, {\href{https://swoc.scriptindia.org}{Script Winter of Code}}, {\href{https://gdsc.community.dev/medi-caps-university-indore}{GDSC Medicaps}}:}
{I've mentored aspiring developers, and designers in hackathons and open-source programs, helping them build innovative projects.}} \vspace{3pt}
              \resumeItem{\textbf{\href{https://devpost.com/software/budgetstay}{Hackathon Winner at HackThisFall for Most Creative Use of Twilio}}} \vspace{3pt}
              \resumeItem{{As a hacker, built a {\textbf{\href{https://devfolio.co/projects/mystic-899b}{{P2P based Play-to-Earn game}}}} in a team at {\textbf{\href{https://ethindia.co/}{{ETHIndia'23}}}} hackathon and won NFTs \& bounties. }} \vspace{3pt} 
    \resumeItemListEnd
  }}
\end{itemize}

\end{document}


%%%%%%%%%%%  RESUME ENDS HERE  %%%%%%%%%%%
%-------------------------------------------
